Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2018-01-10 CCIAQVTS/CCIAQVTS.tex
Improved the flow a tiny bit

    \section{Introduction}
    \label{sec:introduction}
    In recent decades, the technical utility of quantum mechanics has become abundantly clear. In the realm of computation, quantum algorithms --- such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} --- scale exponentially better than their classical counterparts. In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} --- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill. Throughout history, every aspect of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}. Motivated by past successes, a primal objective of modern quantum information theory is the discovery of new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.

    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964,Brunner_2013}. Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}. The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{non-classicality} of a given observation. More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}. Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure. The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}. Causal compatibility inequalities, such as Bell and Instrumental inequalities \cite{pearl1995instrumental,bonet2001instrumental,evans2012graphical}, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation. To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}. The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$. Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}. More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood. Here we investigate one particular correlation scenario named the Triangle structure (\cref{fig:triangle_structure}).

@@

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution first was proven to be non-classical without the use of inequalities. Here we offer a direct proof using inequalities, with the advantage that our proof is robust to noise. A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}. In \cref{sec:violations_noise} we quantify the robustness to noise of the Fritz distribution, and we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new new flavors of non-classicality in the Triangle structure. Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. \Cref{sec:conclusions} concludes with proposed avenues for further research.

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here. The first is to recognize that many equality constraints are implied by the causal structure, including conditional independence relations and so-called Verma constraints among others; see Refs. \cite{evans2015margins,evans2017markov} for thorough treatments. The failure to satisfy an equality constraint immediately disqualifies $\prob[\nodes_{O}]$ from being compatible with $\graph$. Equality constraints are easily derived given a causal structure, and checking equality-constraints satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence. In quantum theory, however, we require strong, more sensitive, causal inference techniques. This is because the equality constraints satisfied by classical correlations (compatible with some classical causal structure) are also all satisfied by quantum correlations (generated by the quantumified causal structure in which latent variables are replaced with shared entanglement) \cite{Henson_2014}.
    Our focus, therefore, in on deriving \emph{inequality} constraints (over $\prob[\nodes_{O}]$ and its marginals) implied by a causal structure, which we term \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}. For some causal structures, the equality constraints associated with it are sufficient to perfectly characterize the distributions genuinely compatible with it; for others, however, inequality constraints are also important. Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell structure, and the Triangle structure studied here, among infinitely many others.
    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:inflation_technique_summary} discusses the Inflation Technique as applied in this work.

@@

    The bipartite Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant parties who observe the outcomes of local measurements as random variables $A (B)$ determined by their individual measurement settings $S_A (S_B)$, and where the parties are also presumed to be commonly informed by some shared latent resource $\la$~\cite{Brunner_2013}. The resulting observable correlations hence naturally form a conditional probability distribution $\prob[AB|S_AS_B]$. Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, $\prob[A|S_A,\la]$ is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}

    \begin{align}\label{eq:bellcompat}
     \prob[AB|S_AS_B] \text{ is classically compatible with \cref{fig:bell_structure}} \quad\iff \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
    \end{align}

@@

    Let us now contrast now the classical definition of compatibility with its quantum generalization. Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems. Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement sets $M_{A|S_A}, M_{B|S_B}$\footnote{Note that a measurement set $M_{A} = \bc{M_{A}^{1}, M_{A}^{2}, \ldots, M_{A}^{k}}$ services a shorthand notation in the following sense, $\prob[A] = \Tr\bs{\rho M_{A}} \implies \prob[A]\br{a} = \Tr\bs{\rho M_{A}^{a}}$.} with indices conditional upon the measurement settings, such that
    \begin{align}\label{eq:bellQcompat}
    \prob[AB|S_AS_B] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
    \end{align}
    The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions. A notable example is the CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original}.
    \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type. Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.

@@

    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}, i.e.
    \[ \prob[ABC] \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\iff\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,. \eq \label{eq:triangle_compatibility} \]
    By contrast, the quantum realization of the Triangle structure are defined with substantially greater freedom, namely
    \[ \prob[ABC] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}}\,, \eq \label{eq:triangle_Qcompatibility} \]
    where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the states and measurements appropriately.

    The Triangle structure serves as an excellent test case for furthering our understanding of quantum non-classicality in network causal structures. It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure. The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
    Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality. It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicality are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of Ref. \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum. The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. In \Cref{sec:preliminary_research} we report on attempts to utilize these inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit non-classical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.

@@

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the previously-published compatibility inequalities of Ref.~\cite{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014} (which had also been investigated numerically independently by \citet{Weilenmann_2016}). This preliminary investigation did not yield interesting solutions, as none of those inequalities were violated by any 2-outcome coarse-graining of the Fritz distribution. These early results suggest that there is no quantum-classical gap in the Triangle structure for \textit{two-outcome} measurements, i.e. \cref{eq:triangle_compatibility} and \cref{eq:triangle_Qcompatibility} define identical sets of binary-outcome tripartite distributions.

@@

    \subsection{The WagonWheel Inequality}
    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
        \eq\label[ineq]{eq:ww_ineq}
        I\tsb{WagonWheel} : \\
        +P_{A_{l}B_{l}}(11) -P_{A_{l}B_{l}C_{l}C_{r}}(1111) +P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) +P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}.
    Aside from increasing outcome cardinality, we are also forced to consider larger inflations than those analyzed in Ref.~\cite{Inflation}. This is because we found the smaller inflations considered there --- such as the Spiral inflation depicted in \cref{fig:spiral_inflation} --- were simply \textit{unable} to witness the incompatibility of the Fritz distribution, even when analyzed explicitly using four possible outcomes for every observable variable.

@@

    It is perhaps curious, however, that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:triangle_Qcompatibility} are restricted to maximally entangled states. This distributions certainly violate $I\tsb{Web}$ more than $\prob[\fritz]$, even it is isn't the global maximum of $I\tsb{Web}$. This finding of more-violation with less-entanglement resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} demonstrating that entanglement and non-classicality are different resources.

@@

    Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure. Currently, it remains speculative about how to recognize whether-or-not a given distribution for the Triangle structure exhibits non-classical correlations of a fundamentally novel qualitative nature than Bell-type non-classicality. We imagine that advantages from a resource perspective might be critical to establish such a novelty signature.
    Perhaps another signature would be if the distribution can arise in the Triangle structure only through the use of of entangled measurements, such as perhaps the conjecture in Ref. \cite{Gisin_2017}. Ultimately, given any said classifier, it remains unclear whether or not such distributions even exist.

>>>>

    \section{Introduction}
    \label{sec:introduction}
    In recent decades, the technical utility of quantum mechanics has become abundantly clear. In the realm of computation, quantum algorithms --- such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} --- scale exponentially better than their classical counterparts. In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} --- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill. Throughout history, every aspect of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}. Motivated by past successes, a primal objective of modern quantum information theory is to discover new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.

    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964,Brunner_2013}. Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}. The enumeration of Bell inequalities has since become a widespread systematic method for demonstrating the \textit{non-classicality} of a given observation. More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}. Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure. The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}. Causal compatibility inequalities, such as Bell and Instrumental inequalities \cite{pearl1995instrumental,bonet2001instrumental,evans2012graphical}, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation. To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}. The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$. Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}. More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood. Here we investigate one particular correlation scenario named the Triangle structure (\cref{fig:triangle_structure}).

@@

    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used. \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities. \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying. \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}. The Fritz distribution first was proven to be non-classical without the use of inequalities. Here we offer a direct proof using inequalities, with the advantage that our proof is robust to noise. A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}. In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. Additionally, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new flavors of non-classicality in the Triangle structure. \Cref{sec:conclusions} concludes with proposed avenues for further research.

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here. The first is to recognize that many equality constraints are implied by the causal structure, including conditional independence relations and so-called Verma constraints among others; see Refs. \cite{evans2015margins,evans2017markov} for thorough treatments. The failure to satisfy an equality constraint immediately disqualifies $\prob[\nodes_{O}]$ from being compatible with $\graph$. Equality constraints are easily derived given a causal structure, and checking equality-constraints satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence. In quantum theory, however, we require strong, more sensitive, causal inference techniques. This is because the equality constraints satisfied by compatible classical correlations are also all satisfied by quantum correlations \cite{Henson_2014}.
    Our focus, therefore, in on deriving \emph{inequality} constraints (over $\prob[\nodes_{O}]$ and its marginals) implied by a causal structure, which we term \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}. For some causal structures, the equality constraints associated with it are sufficient to perfectly characterize the distributions genuinely compatible with it; for others, however, inequality constraints are also important. Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell structure, and the Triangle structure studied here, among infinitely many others.
    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:inflation_technique_summary} discusses the Inflation Technique as applied in this work.

@@

    The bipartite Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant parties who observe the outcomes of local measurements as random variables $A,B$ determined by their individual measurement settings $S_A,S_B$, and where the parties are also presumed to be commonly informed by some shared latent resource $\la$~\cite{Brunner_2013}. The observed correlations naturally form a conditional probability distribution $\prob[AB|S_AS_B]$. Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, $\prob[AB|S_AS_B]$ is compatible with \cref{fig:bell_structure} if and only if there exists some distribution $\prob[\la]$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}

    \begin{align}\label{eq:bellcompat}
     \prob[AB|S_AS_B] \text{ is classically compatible with \cref{fig:bell_structure}} \quad\iff \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\prob[\la]\,.
    \end{align}

@@

    Let us now contrast the classical definition of compatibility with its quantum generalization. Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems. Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement sets $M_{A|S_A}, M_{B|S_B}$\footnote{Note that a measurement set $M_{A} = \bc{M_{A}^{1}, M_{A}^{2}, \ldots, M_{A}^{k}}$ services a shorthand notation in the following sense, $\prob[A] = \Tr\bs{\rho M_{A}} \implies \prob[A]\br{a} = \Tr\bs{\rho M_{A}^{a}}$.} with indices conditional upon the measurement settings, such that
    \begin{align}\label{eq:bellQcompat}
    \prob[AB|S_AS_B] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
    \end{align}
    The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions. A notable example is the CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original}.
    \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type. Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.

@@

    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum_{X,Y,Z}$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}, i.e.
    \[ \prob[ABC] \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\iff\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,. \eq \label{eq:triangle_compatibility} \]
    By contrast, the quantum realization of the Triangle structure are defined with substantially greater freedom, namely
    \[ \prob[ABC] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}}\,, \eq \label{eq:triangle_Qcompatibility} \]
    where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the underlying tensor structure of the states and measurements appropriately.

    The Triangle structure serves as an excellent test case for furthering our understanding of quantum non-classicality in network causal structures. It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure. The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
    Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality. It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicality are expected to correspond to novel information-theoretical quantum advantages. A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
    Some inequality constraints for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor. \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}. Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure. In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum. The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution. That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts. \Cref{sec:preliminary_research} reports our attempt to utilize these aforementioned inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches effectively motivates the remainder of this work.
    In summary, the Triangle structure is a desirable case study because it is known to admit non-classical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions. This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.

@@

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the previously-published compatibility inequalities of~\cite{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014} (which had also been investigated numerically independently by \citet{Weilenmann_2016}). This preliminary investigation did not yield interesting solutions, as none of those inequalities were violated by any 2-outcome coarse-graining of the Fritz distribution. These early results suggest that there is no quantum-classical gap in the Triangle structure for \textit{two-outcome} measurements, i.e. \cref{eq:triangle_compatibility} and \cref{eq:triangle_Qcompatibility} define identical sets of binary-outcome tripartite distributions.

@@

    \subsection{The WagonWheel Inequality}
    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
        \eq\label[ineq]{eq:ww_ineq}
        I\tsb{WagonWheel} : \\
        +P_{A_{l}B_{l}}(11) -P_{A_{l}B_{l}C_{l}C_{r}}(1111) +P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) +P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}.
    Aside from increasing outcome cardinality, we are also forced to consider larger inflations than those analyzed in~\cite{Inflation}. This is because we found the smaller inflations considered there --- such as the Spiral inflation depicted in \cref{fig:spiral_inflation} --- were simply \textit{unable} to witness the incompatibility of the Fritz distribution, even when analyzed explicitly using four possible outcomes for every observable variable.

@@

    It is perhaps curious, however, that violation achieved by the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:triangle_Qcompatibility} are restricted to maximally entangled states. This finding of more-violation with less-entanglement resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} demonstrating that entanglement and non-classicality are different resources.

@@

    Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure. Currently, it remains speculative about how to recognize whether-or-not a given distribution for the Triangle structure exhibits non-classical correlations of a fundamentally novel qualitative nature than Bell-type non-classicality. We imagine that advantages from a resource perspective might be critical to establish such a novelty signature.
    Perhaps another signature would be if the distribution can arise in the Triangle structure only through the use of of entangled measurements, such as perhaps the conjecture in \cite{Gisin_2017}. Ultimately, given any said classifier, it remains unclear whether or not such distributions even exist.
